---
title: "Final Slidify Data Science Capstone"
author: "Chongyuan Xu"
highlighter: highlight.js
output: pdf_document
job: Postdoctor
knit: slidify::knit2slides
mode: selfcontained
hitheme: tomorrow
subtitle: A Method to Predict Stars by a Review of a Business
framework: io2012
widgets: []
---

## The Questions to Answer

The following table demonstrates the number of each stars rated by customers from the historical review data. 

```{r, echo = FALSE}
table(review$stars)
```

So it is intersting to find what is the relationship between the review and its rate? What are the most frequent positive and negative words in the reviews? 

--- .class #id 

## The Most Frequent Positive and Negative Words

I use NLP algorithms to find the common words and they can be seen in the following barplots. 

```{r, echo = FALSE}
par(mfrow = c(2, 2))
barplot(singlePositive[1 : min(10, length(singlePositive))], main = "Top Frequent Positive Single Words", cex.main = 1, cex.axis = 0.75, las = 2)
barplot(singleNegative[1 : min(10, length(singleNegative))], main = "Top Frequent Negative Single Words", cex.main = 1, cex.axis = 0.75, las = 2)
barplot(doublePositive[1 : min(10, length(doublePositive))], main = "Top Frequent Positive Double Words", cex.main = 1, cex.axis = 0.75, las = 2)
barplot(doubleNegative[1 : min(10, length(doubleNegative))], main = "Top Frequency Negative Double Words", cex.main = 1, cex.axis = 0.75, las = 2)
```

--- .class #id

## The Grade Predicted by any Review Text

I create the word frequency matrix first and then design an algorithm based on SVM to predict the grade by text data according to machine learning techniques. 

```{r, echo = FALSE}
confusionMatrix(predict, data$stars)
```

--- .class #id

## Results and Future Works

It is seen that the accuracy is just 70 percent, although it is the highest algorithm among my experimental results. To be honest, this is not a bad result. However, we still need to research some new tools to improve the accuracy. 



